% Created 2023-03-22 Wed 18:32
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Reyva Babtista}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Reyva Babtista},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{morrisonTigerAwareInnovativeMobile2018}
\label{sec:org5357e54}
\subsection{foo}
\label{sec:org25b281b}
\subsection{bar}
\label{sec:org76aee0d}
\subsection{This is where its get interesting}
\label{sec:orgd3bfccb}
\subsection{Skeleton}
\label{sec:org10cd59b}
\subsubsection{Highlight on page 1}
\label{sec:orgaf0003a}
\begin{enumerate}
\item Contents
\label{sec:orgb3aeeb1}
Abstract—From health to community assessment,
\end{enumerate}
\subsubsection{Highlight on page 1}
\label{sec:org448400c}
\begin{enumerate}
\item Contents
\label{sec:orgef2a2e9}
innovative system called TigerAware is presented
to address this issue. TigerAware
\end{enumerate}
\subsubsection{Highlight on page 1}
\label{sec:orgb9cc7d4}
\begin{enumerate}
\item Contents
\label{sec:org7f76ac7}
To greatly reduce the software development
and budgetary restrictions and provide more ﬂexibility and
capability for researchers conducting smart-phone-based re-
search, we developed TigerAware,
\item Comment
\label{sec:orgc939f88}
test
\end{enumerate}
\subsubsection{Text note on page 1}
\label{sec:org6b63fae}
\begin{enumerate}
\item Contents
\label{sec:org03ae06c}
search, we developed TigerAware, a multi-tenanted platform
for researchers to easily author, deploy, and manage survey
and sensor-data based studies.
TigerAware can be easily incorporated into a ﬁeld study
with little modiﬁcations to the existing work ﬂow and reduces
the necessity of allocating signiﬁcant funds for development
of the IT system. Furthermore, the platform is highly con-
ﬁgurable, allowing researchers to integrate novel data sources
and interfaces. As an example, we recently integrated a blood
alcohol level data type and and voice based assistant interface
with minimal effort.
TigerAware has signiﬁcant advantages over previous com-
mercial and academic research data collection platforms. By
including existing state-of-the-art features and considering
various sensors used in a range of existing research studies,
we were able to greatly improve upon existing platforms. In
addition, data collected from the sensors and survey responses
can be visualized on TigerAware’s dashboard in real time.
As a result, TigerAware is developed to offer a generic,
customizable survey creation, deployment, and survey data
and sensor data collection capability for researchers who
want to use mobilephone-based surveys in conjunction with
various internal or external data sources, including wireless
and wearable sensors and Internet of Things (IoT) devices.
TigerAware is highly modular and uses advanced web and
mobile technologies to incorporate diverse data sources with a
rich set of survey question types, requireing little development
work by researchers for their studies. TigerAware has been
applied to a focus group and several pilot studies and shown
excellent capabilities to be easily adapted and deployed for
new types of data collection tasks and a wide range of studies.
Overall, contributions of this work include a powerful new
Abstract—From health to community assessment, mobile
phones have become a cornerstone of data collection across
many areas of research. However, mobile phone-based studies
are difﬁcult to develop and deploy, often requiring in house
development teams and large portions of research budgets. In
this paper, an innovative system called TigerAware is presented
to address this issue. TigerAware is developed to offer a generic
and customizable tool, which allows researchers to create surveys
to collect a wide range of data, including but not limited to
question responses, on device sensor data, such as GPS d
\end{enumerate}
\end{document}